\begin{thebibliography}{10}
\addcontentsline{toc}{chapter}{\numberline{}References}

\bibitem{bhope2019webpush}
Rahul Atul Bhope, “Computer Vision based drowsiness detection for motorized vehicles with Web Push Notifications”, IEEE 4th International Conference on Internet of Things, IEEE, Ghaziabad, India, 2019.

\bibitem{wijnands2019mobile3d}
Jasper S. Wijnands, Jason Thompson, Kerry A. Nice, Gideon D. P, Aschwanden & Mark Stevenson, “Real-time monitoring of driver drowsiness on mobile platforms using 3D neural networks”, Neural Computing and Applications, 2019.

\bibitem{schwarz2019dms}
Chris Schwarz, John Gaspar, Thomas Miller & Reza Yousefian, “The detection of drowsiness using a driver monitoring system”, Journal of Traffic Injury Prevention (Taylor and Francis Online), 2019.

\bibitem{ranjan2020cv}
Aditya Ranjan, Karan Vyas, Sujay Ghadge, Siddharth Patel, Suvarna Sanjay Pawar, “Driver Drowsiness Detection System Using Computer Vision.”, International Research Journal of Engineering and Technology(IRJET), 2020.

\bibitem{mohana2019eyemouth}
B. Mohana, C. M. Sheela Rani, “Drowsiness Detection Based on Eye Closure and Yawning Detection”, International Research Journal of Engineering and Technology(IRJET), 2019.

\bibitem{dac2016manual}
Driver Alert Control (DAC). (2016, Feb 10). Retrieved from http://support.volvocars.com/uk/cars/Pages/owners-manual.aspx?mc=Y555&my=2015&sw=14w20&article=2e82f6fc0d1139c2c0a801e800329d4e
\newpage

\bibitem{mardi2011chaoticEEG}
Z. Mardi, S. N. Ashtiani, and M. Mikaili, “EEG-based drowsiness detection for safe driving using chaotic features and statistical tests,” Journal of Medical Signals and Sensors, vol. 1, pp. 130–137, 2011.

\bibitem{danisman2010blink}
T. Danisman, I.M. Bilasco, C. Djeraba and N. Ihaddadene, “Drowsy driver detection system using eye blink patterns,” Universite Lille 1 & Telecom Lille 1, Marconi, France, 2010.

\bibitem{hariri2011yawn}
B. Hariri, S. Abtahi, S. Shirmohammadi, and L. Martel, “A yawning measurement method to detect driver drowsiness,” Distributed and Collaborative Virtual Environments Research Laboratory, University of Ottawa, Ottawa, ON, Canada, 2011.

\bibitem{li2009yawncameras}
Li, Y. Chen and Z. Li, "Yawning detection for monitoring driver fatigue based on two cameras", Proceedings of the 12th International IEEE Conference Intelligent Transportation Systems., pp. 1-6, Oct. 2009.

\end{thebibliography}
